---
title: "Exam 2"
author: 'Heather Qiu'
date: "11/26/2019"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
library(rlist)
library(knitr)
library(shiny)
library(shinythemes)
library(DT)

knitr::opts_chunk$set(echo = TRUE, comment = NA, 
                      message = FALSE, warning = FALSE)
```

### example keys:
key1: 42fef648a7b340cda283c54b25488ee1; key2: 7b4874cf736f4069bcb0c7e466e91898; key3: 87576c02b91346cf9343ef71d176809f

## Task 1
1. Get all the news sources categorized as general or business, where the language is English and the country is United States. Filter the result to obtain the ids for CNN, Fox News, The Wall Street Journal, and Reuters.

```{r}
base_url <- "https://newsapi.org/v2/"

#function to get news sources with given condition
get_data1 <- function(category) {
  query <- str_c("sources?language=en&country=us&category=", 
                 category, "&apiKey=7b4874cf736f4069bcb0c7e466e91898")
  fromJSON(str_c(base_url, query))$sources
}

type <- c("general", "business")
#get the required news sources df
news.source <- map_df(type, get_data1)

#filtering the id df
target.name = c("CNN","Fox News","The Wall Street Journal","Reuters")
df1 <- news.source %>% 
  filter(name %in% target.name) %>% 
  select(name, id)

kable(df1)
```

According to this question, CNN, Fox News, The Wall Street Journal, and Reuters are United States news Sources with English language.




2. Get the most recent headline title from CNN, Fox News, The Wall Street Journal, and Reuters about "taxes", where the country is United States.

Basing on diffrent understandings of this question, there are two answers.

Answer 1: the most recent headline title from the four sources of articles about "taxes"

```{r}
#function to get articles with the given condition
get_data2 <- function(source) {
  query <- str_c("everything?q=taxes&sortBy=publishedAt&sources=", 
                 source, "&apiKey=7b4874cf736f4069bcb0c7e466e91898")
  fromJSON(str_c(base_url, query),flatten = TRUE)$articles[1,] #only include the most recent one
}

ids = df1$id
#get the required headline title df
news.headline1 <- map_df(ids, get_data2) %>% 
  select(title, publishedAt, source.name)

kable(news.headline1)
```

Answer 2: the most recent "top" headline title from the four sources of articles about "taxes"

```{r}
#function to get top headlines with the given condition
get_data2.2 <- function(source) {
  query <- str_c("top-headlines?q=taxes&sources=", 
                 source, "&apiKey=7b4874cf736f4069bcb0c7e466e91898")
  # Articles are sorted by the earliest date published first by default.
  
  fromJSON(str_c(base_url, query),flatten = TRUE)$articles
}

ids = df1$id
#get the required headline title df: results number is 0
news.headline1.2 <- map_df(ids, get_data2.2)
nrow(news.headline1.2)
```





3. Get the headline titles from CNN, Fox News, The Wall Street Journal, and Reuters on 11-01-19, where "healthcare" was in the title, the country is United States, and language is English.

```{r}
#function to match titles with given condition
get_data3 <- function(source) {
  query <- str_c("everything?qInTitle=healthcare&from=2019-11-01&to=2019-11-01&sources=", 
                 source, "&apiKey=7b4874cf736f4069bcb0c7e466e91898")
  fromJSON(str_c(base_url, query),flatten = TRUE)$articles
}

#get the required headline title df
news.headline2 <- map_df(ids, get_data3) %>%
  select(title, publishedAt, source.name)

kable(news.headline2)
```






## Task 2
For all functions, sources should only be a subset of CNN, Fox News, The Wall Street Journal, and Reuters. The country will always be United States, and the language will always be English. Other request parameters you see in the API documentation and not specified above are not required to be included in your wrapper functions as parameters.
Each function should return a tidy data frame.
Each function should include basic ??input checks.

1. Create get_sources() with arguments category and api_key. This function serves as a wrapper for News API's "Sources" endpoint.

```{r, helper function for sources}
get_sources_helper <- function(category, api) {
  base_url <- "https://newsapi.org/v2/sources?language=en&country=us"
  query <- str_c("&category=", category, "&apiKey=", api)
  fromJSON(str_c(base_url, query))$sources
}
```

```{r, sources function}
# main function
get_sources <- function(category=c("business", "entertainment", "general",
                                   "health", "science", "sports", "technology"),
                        api_key) {
  target.name = c("business", "entertainment", "general",
                  "health", "science", "sports", "technology")
  #input check
  stopifnot(nchar(api_key) == 32)
  stopifnot(category %in% target.name)
  
  map_df(category, get_sources_helper, api=api_key)
}
```

```{r}
# example
eg.s1 <- get_sources(category="business", api_key="7b4874cf736f4069bcb0c7e466e91898")
kable(eg.s1)
```






2. Create get_headlines() with arguments sources, q, page_size, page, and api_key. This function serves as a wrapper for News API's "Top headlines" endpoint.

```{r, helper function for headlines}
get_headlines_helper <- function(id, query, ps, p, api) {
  base_url <- "https://newsapi.org/v2/top-headlines?"
  
  if (is.null(query)) {
    query1 <- str_c("sources=", id, "&pageSize=", ps, "&page=", p, "&apiKey=", api)
  }
  else {
    query1 <- str_c("q=", query, "&sources=", id, "&pageSize=", ps, "&page=", p, "&apiKey=", api)
  }
  
  fromJSON(str_c(base_url, query1), flatten = TRUE)$articles
}
```


```{r, headline function}
# main function
get_headlines <- function(sources=c("CNN", "Fox News", "The Wall Street Journal", "Reuters"), 
                          q=NULL, page_size=NULL, page=NULL, api_key) {
  target.name = c("CNN", "Fox News", "The Wall Street Journal", "Reuters")
  
  #api check
  stopifnot(nchar(api_key) == 32)
  
  #set default page_size and page number
  if (is.null(page_size)) {page_size <- 20}
  if (is.null(page)) {page <- 1}
  
  #input check
  stopifnot(sources %in% target.name)
  stopifnot(page_size <= 100 && page_size > 0 && page > 0)
  stopifnot(page_size == as.integer(page_size) && page == as.integer(page))
  
  #extract ids for sources
  ids.full=c("cnn", "fox-news", "reuters", "the-wall-street-journal")
  ids=ids.full[which(sources == target.name)]
  
  map_df(ids, get_headlines_helper, query=q, ps=page_size, p=page, api=api_key)
}
```


```{r}
# examples
eg.h1 <- get_headlines(sources="Fox News", api_key="7b4874cf736f4069bcb0c7e466e91898")
eg.h2 <- get_headlines(sources="Fox News", page_size=2, page=2, 
                       api_key="7b4874cf736f4069bcb0c7e466e91898")

kable(eg.h1 %>% select(author, title) %>% head(5))
kable(eg.h2 %>% select(author, title))
```






3. Create get_historic() with arguments q, q_title, sources, from, to, sort_by, page_size, page, api_key. This function serves as a wrapper for News API's "Everything" endpoint.

```{r, helper function for everything}
get_historic_helper <- function(id, query, qt, f, t, st, ps, p, api) {
  base_url <- "https://newsapi.org/v2/everything?"
  
  if(is.null(query) && is.null(qt)){
    query1 <- str_c("sources=", id, "&from=", f, 
                  "&to=", t, "&sortBy=", st, "&pageSize=", ps, "&apiKey=", api)
  }
  if(!is.null(query) && is.null(qt)){
    query1 <- str_c("q=", query, "&sources=", id, "&from=", f, 
                  "&to=", t, "&sortBy=", st, "&pageSize=", ps, "&apiKey=", api)
  }
  if(is.null(query) && !is.null(qt)){
    query1 <- str_c("qInTitle=", qt, "&sources=", id, "&from=", f, 
                  "&to=", t, "&sortBy=", st, "&pageSize=", ps, "&apiKey=", api)
  }
  if(!is.null(query) && !is.null(qt)){
    query1 <- str_c("q=", query, "&qInTitle=", qt, "&sources=", id, "&from=", f, 
                  "&to=", t, "&sortBy=", st, "&pageSize=", ps, "&apiKey=", api)
  }
  
  fromJSON(str_c(base_url, query1), flatten = TRUE)$articles
}
```


```{r, everything function}
# main function
get_historic <- function(sources=c("CNN", "Fox News", "The Wall Street Journal", "Reuters"), 
                          q=NULL, q_title=NULL, from=NULL, to=NULL, sort_by="publishedAt",
                         page_size=NULL, page=NULL, api_key) {
  #api check
  stopifnot(nchar(api_key) == 32)
  
  target.name = c("CNN", "Fox News", "The Wall Street Journal", "Reuters")
  target.sort = c("relevancy", "popularity", "publishedAt")
  # set default from (a month before), to (today)
  if (is.null(from)) {from <- Sys.Date()-31} 
  if (is.null(to)) {to <- Sys.Date()}
  #set default page_size and page number
  if (is.null(page_size)) {page_size <- 20}
  if (is.null(page)) {page <- 1}
  
  #input check
  stopifnot(sources %in% target.name && sort_by %in% target.sort) 
  stopifnot(page_size <= 100 && page_size > 0 && page > 0)
  stopifnot(page_size == as.integer(page_size) && page == as.integer(page))
  stopifnot(as.Date(from) >= Sys.Date()-31 && as.Date(to) <= Sys.Date())
  
  #extract ids for sources
  ids.full=c("cnn", "fox-news", "reuters", "the-wall-street-journal")
  ids=ids.full[which(sources == target.name)]
  
  map_df(ids, get_historic_helper, query=q, qt=q_title, f=from,
         t=to, st=sort_by, ps=page_size, p=page, api=api_key)
}
```


```{r}
# example
eg.his1 <- get_historic(sources="Fox News", q="taxes", from="2019-11-20",
             api_key="7b4874cf736f4069bcb0c7e466e91898")
kable(eg.his1 %>% select(author, title))
```


## Task 3

Shiny App:

```{r}
createLink <- function(val, namet) {
  sprintf(paste0('<a href="', URLdecode(val),'" target="_blank">', namet ,'</a>'))
}

#reference link:
#https://stackoverflow.com/questions/44571001/shiny-display-urls-in-datatable?noredirect=1&lq=1
```


```{r}
ui <- shinyUI(
  navbarPage(theme = shinytheme("united"),
             "Central News Hub",
            # panel: the search type is sources
            tabPanel("Sources",
            sidebarLayout(
              sidebarPanel(width = 4,
               # api input box
               textInput("api1", 
                         label = "API key",
                         value = "Enter api key here:"),
               
               checkboxGroupInput("category", 
                                  "News Sources Category:",
                                  choices = c("business", "entertainment", "general", 
                                              "health", "science", "sports", "technology"),
                                  selected = "business"),
                 # action button
                 actionButton("search1", "Search Sources")
               ),
              mainPanel(
                tabsetPanel(type = "tabs",
                            tabPanel(title = "Main Information", dataTableOutput("table1"))
                )##tabsetPanel
              )
              )##sidebarPanel
            ), ##tabPanel sources
               
           # panel: the search type is headlines
           tabPanel("Headlines",
           sidebarLayout(
             sidebarPanel(width = 4,
             # api input box
             textInput("api2", 
                       label = "API key",
                       value = "Enter api key here:"),

             checkboxGroupInput("sources_headlines", 
                                "News sources:",
                                c("CNN", "Fox News", "The Wall Street Journal", "Reuters"),
                                selected = "CNN"),
             textInput("query_headlines",
                       "Keywords:"),
             numericInput("page_size_headlines", 
                          label = "Results Shown per Page:",
                          value = 20, min = 1, max = 100, step = 1),
             numericInput("page_headlines",
                          label = "Page Number:",
                          value = 1, min = 1, step = 1),
             # action button
             actionButton("search2", "Search Headlines")
           ),
           mainPanel(
                tabsetPanel(type = "tabs",
                            tabPanel(title = "Main Information", dataTableOutput("table2")),
                            tabPanel(title = "Description", tableOutput("table2_2"))
                            
                )##tabsetPanel
              )
              )##sidebarPanel
            ), ##tabPanel headlines
           
           # panel: search type is historic
           tabPanel("Historic",
           sidebarLayout(
             sidebarPanel(width = 4,
             # api input box
             textInput("api3", 
                       label = "API key",
                       value = "Enter api key here:"),
         
             checkboxGroupInput("sources_historic", 
                                "News sources:",
                                c("CNN", "Fox News", "The Wall Street Journal", "Reuters"),
                                selected = "CNN"),
             dateRangeInput("dates",
                            label = "Date range",
                            min = Sys.Date()-31,
                            max = Sys.Date()),
             selectInput("sort_by", 
                         "Results sort by:",
                         c("relevancy", "popularity", "publishedAt")),
             textInput("query_historic",
                       "Keywords for title and body:"),
             textInput("query_title_historic",
                       "Keywords for title only:"),
             numericInput("page_size_historic", 
                          label = "Results Shown per Page:",
                          value = 20, min = 1, max = 100, step = 1),
             numericInput("page_historic",
                          label = "Page Number:",
                          value = 1, min = 1, step = 1),
             # action button
             actionButton("search3", "Search Historic")
           ),
           mainPanel(
                tabsetPanel(type = "tabs",
                            tabPanel(title = "Main Information", dataTableOutput("table3")),
                            tabPanel(title = "Description", tableOutput("table3_2")),
                            tabPanel(title = "Content", tableOutput("table3_3"))
                )##tabsetPanel
              )
              )##sidebarPanel
            ) ##tabPanel historic

  )# navbarPage
) # shinyUI

server <- function(input, output) {
  
  data1 <- eventReactive(input$search1, {
    get_sources(input$category, input$api1)
  })
  
  data2 <- eventReactive(input$search2, {
    get_headlines(input$sources_headlines, input$query_headlines,
                  input$page_size_headlines, input$page_headlines, input$api2)
  })
  
  data3 <- eventReactive(input$search3, {
    get_historic(input$sources_historic, input$query_historic,
                 input$query_title_historic, as.character(input$dates[1]),
                 as.character(input$dates[2]), input$sort_by, input$page_size_historic,
                 input$page_historic, input$api3)
  })
  
  # table output for dataframe
  output$table1 <- renderDataTable({
    sources.df <- data1()
    if (nrow(sources.df) == 0) {print("no results found")}
    else {
      sources.df %>% 
        mutate(name = createLink(sources.df$url, name)) %>% 
        select(name, category, description)
    }
  }, escape = FALSE)
  
  output$table2 <- renderDataTable({
    headlines.df <- data2()
    if (nrow(headlines.df) == 0) {print("no results found")}
    else {
      headlines.df %>% 
        mutate(title = createLink(headlines.df$url, title)) %>% 
        select(title, author, publishedAt)
    }
  }, escape = FALSE)
  
  output$table2_2 <- renderTable({
    headlines.df <- data2()
    if (nrow(headlines.df) == 0) {print("no results found")}
    else {
      headlines.df %>% select(title, description)
    }
  })
  
  output$table3 <- renderDataTable({
    historic.df <- data3()
    if (nrow(historic.df) == 0) {print("no results found")}
    else{
      historic.df %>%
        mutate(title = createLink(historic.df$url, title)) %>% 
        select(source.name, title, author, publishedAt)
    }
  }, escape = FALSE)
  
  output$table3_2 <- renderTable({
    historic.df <- data3()
    if (nrow(historic.df) == 0) {print("no results found")}
    else {
      historic.df %>% select(title, description)
    }
  })
  
  output$table3_3 <- renderTable({
    historic.df <- data3()
    if (nrow(historic.df) == 0) {print("no results found")}
    else {
      historic.df %>% select(title, content)
    }
  })
  
}

shinyApp(ui = ui, server = server)
```





